Adaptive broadcast tree for multicores

### 2013-06-03 paper.tex
First thoughts and start of implementation for Fibonacci trees

Several optimizations are possible. First, nodes further up the tree
should have a higher degree i.e.\ send more messages so that they do
not idle~\cite{Bar-Noy1994}. An example of such a tree is a Fibonacci
tree.

>>>>

Several optimizations are possible. First, nodes further up the tree
should have a higher degree i.e.\ send more messages so that they do
not idle~\cite{Bar-Noy1994}. An example of such a tree is a Fibonacci
tree, which is known to be optimal for the case that send and receive
time are equal~\cite{Bar-Noy1994}.

In contrast, we assume that the model is given, which allows us to
simulate sending messages along the broadcast tree. Whenever a node is
idle in the model, it will send a message to one of the cores, that
did not receive any messages yet. For the special case that send
equals receive time, this should also yield a Fibonacci tree.
